---
title: "Discussion Board Week 11"
author: "Al Haque"
date: '2022-10-31'
output: html_document
---

```{r include= FALSE}
library(tidyverse)
```

### Reading the data
This dataset I found on kaggle after browsing google for dataset that I can create a linear regression for. This dataset contains 
rows of houses in Taiwan that gives information about the house,its distance from MRt,longitude and latitude and the price.I
created a regression model where it creates a model on the input(The age of the house) and it predicts the output(price of the house)


```{r}
Data <- read.csv("https://raw.githubusercontent.com/AldataSci/LinearRegressionAnalysis/main/Real%20estate.csv",header=TRUE)
head(Data)
```


### Building the Model

```{r}
## lets build a simple regression model where we try to predict the price of the house with the age of the house as a predictor..
## lets make meaningful column names!
colnames(Data) <- c("Index","Transaction_Date","House_Age","distance_to_nearest MRT station","#of_convience_stores","latitude","longitude","Price_of_Unit")
head(Data)
```
```{r}
## lets create a simple linear regression model where the inputs for the model is the age of the house and the output are the price of the unit
house_model <- lm(Data$Price_of_Unit ~ Data$House_Age,data = Data)
```


```{r}
## The equation of the regression model is: price of the house = 42.4347 -0.2515 * House_Age
house_model
```

### Visualizing the Data

```{r}
plot(Data$Price_of_Unit ~ Data$House_Age,data = Data)
abline(house_model)
```


### Interpreting the model

```{r}
## The median is somewhat near 0 and the age of the age plays a big factor in the price of the house which may suggest that 
## the age of house plays a role in the price of the house but the R^2 is a really small value which shows that the model may not be 
## a fit the data at all. 
summary(house_model)
```

-----

### Residual Analysis:

```{r}
## There is no clear trend within our residuals this may suggest that the predictor of the age of the house may be useful 
## in sufficently and explaining the data. (pg 23 in textbook)
plot(fitted(house_model),resid(house_model))
```

-----

### Q-Q plots

```{r}
## we can create a qqplot to determine if the model fits the data well, we should expect to see the residuals to be normally
#distributed
qqnorm(resid(house_model))
qqline(resid(house_model))
```

There are some slight divergence at the front end and at the bottom end, the tail front left tail is "lighter" than what we expected
and some of the observation on the right tail is "heavier" than what we expected.

----

